Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-21 main_paper.tex
Tweak statements and presentation of main results

\begin{assumption}[Kernel]\label{A2}
 For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \mathbbm{R}$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
\end{assumption}

@@

\begin{assumption}[Bandwidth]\label{A3}
Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$ and
$n h_n$, $n b_n \to \infty$ as $n \to \infty$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
\end{assumption}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component and
this estimator converges to zero fast enough in probability that it can be be
used as a correction.

\begin{lemma}\label{L1}
  Let $\hat\Delta^*$ be the bias estimator defined in Equation~\eqref{eq:4}.
  Under Assumptions~\ref{A1} and~\ref{A3},
  \[
    \hat\Delta - \big[\E(\hat\tau) - \tau\big] = o_p(-).
  \]
\end{lemma}

@@

Under the same assumptions as earlier, this procedure produces asymptotically
valid confidence intervals.
\begin{theorem}
  Suppose Assumptions~\ref{A1} and~\ref{A3} hold and let $\hat \ell(\alpha)$ and
  $\hat u(\alpha)$ be the interval endpoints produced by Algorithm~\ref{Alg2}
  for some $\alpha \in (0,1)$. Also let $\Pr_\tau$ represent the probability
  distribution of the random variables under the assumption that $\tau$ is
  the true value of the ATE. Then
  \begin{equation}
    \label{eq:5}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Each of the one-sided intervals is asymptotically valid as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}

>>>>

\begin{assumption}[Kernel]\label{A2}
 For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \RR$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
\end{assumption}

@@

\begin{assumption}[Bandwidth]\label{A3}
Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$,
$n h_n$, $n b_n \to \infty$ as $n \to \infty$, and $h_n \leq b_n$ for all $n$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
\end{assumption}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\hat\Delta$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\hat\Delta_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\hat\Delta = \plim_{B_1 \to \infty} \hat\Delta_{B_1}$

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component and
this estimator converges to zero fast enough in probability that it can be be
used as a correction. As is standard in the bootstrap literature, we will assume
that the number of bootstrap replications, $B_1$, is large enough that the
simulation error can be ignored.

\begin{lemma}\label{L1}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\hat\Delta = \E \hat\tau - \tau + o_p()$.
\end{lemma}

@@

As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
error can be ignored. Define the limiting values
\begin{align*}
\hat\Delta^* &= \plim_{B_1,B_2 \to \infty} \hat\Delta^*_{B_1,B_2} \\
\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
\end{align*}
Two results follow. The first is that the secondary bootstrap step produces
a consistent estimator of the bias under the bootstrap distribution. The
second is that the intervals overall are asymptotically valid.

\begin{lemma}\label{L2}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\hat\Delta^* = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
\end{lemma}

\begin{theorem}\label{T1}
  Let $\Pr_\tau$ represent the probability distribution of the random variables
  under the assumption that $\tau$ is the true value of the ATE and suppose
  Assumptions~\ref{A1} and~\ref{A3} hold. Then
  \begin{equation}
    \label{eq:5}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Both of the one-sided intervals are asymptotically valid under the same
  assumptions as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}
